\section{Negative correlation: a potential approach}
The result of the previous section is somewhat discouraging. In this section we attempt to further strengthen the assumptions and show that in case of negative per-item correlation, granted practically not as interesting, a constant POA bound holds. We present a potential approach for proving this result and discuss the complications.

We start with clarifying exactly what we mean by negative correlation. We assume that for every item $j$ and every two players $i$ and $i'$ $\EE_{v_j}[v_{ij}|v_{i'j}=x]$ is a non-increasing function. We also assume as previously that valuations for different items do not correlate: $cov(v_{ij},v_{ik})\neq 0$ for $k\neq j$.

Consider the following deviation for a player who has a value profile $v_i$: for each $k\neq i$ sample $v_{kj}'\sim F_{kj}(v_{kj})$ \textbf{independently of each other,without conditioning on $\mathbf{v_i}$}, and bid $b_{ij}^*(v_i) = x^*_{ij}(v_i,v_{-i}')$ (Here $F_{ij}$ is distribution $F(v)$ integrated over all other than $v_{ij}$ arguments).We have:

$$u_i(b^*(v_i,v_{-i}'),v_{-i}) = \sum_j \left ( \frac{v_{ij}}{2}-\max_{k\neq i}[b_{ij}(v_k)]\right)x_{ij}(v_i,v_{-i}')$$


\begin{conjecture}
For any distribution $F(v)$, and corresponding marginalized distributions $F_{ij}(v_{ij})$ we have

$$\EE_{v_{ij}\sim F_{ij}\ \forall i,j} \sum_{i,j} v_{ij}x^*(v)\geq \frac{1}{2}\EE_{v \sim F(v)}  \sum_{i,j} v_{ij}x^*(v)$$
\end{conjecture}



\begin{conjecture}
Under negatively correlated values in any equilibrium $\max_{k\neq i}[b_{ij}(v_k)]$ and $x_{ij}(v_i,v_{-i}')$ are negatively correlated.
\end{conjecture}
The conjecture seems to hold in a few of our computational experiments, which we designed to test out the worst case scenario, namely when original distribution $F$ is such that every item always has non-zero value for only one player and all items always can be matched to players (this makes optimal welfare with correlation to differ from that without correlation as much as possible). Unfortunately we haven't had enough time to try the prove the statement.
\textit{Discussion} Notice that $x_{ij}(v_i,v_{-i}')$ can be averaged over $v_{-i}'$, because they are independent of $v$, and the result is non-decreasing function in $v_{ij}$ and non-increasing function of $v_{i,j'}$ for $j'\neq j$. So essentially we need to show that maximum bid of other players on item $j$ is negatively correlated with $v_{ij}$ and positively correlated with $v_{ij'}$. This sounds reasonable, but one needs to somehow employ the assumption of equilibrium in order to reason about the function $b(v)$.
\bigskip
\newline Suppose the conjectures are in fact true. We then have

$$\EE_{v_{-i}\sim F(v|v_i)}u_i(b^*(v_i,v_{-i}'),v_{-i}) \geq \sum_j \left ( \frac{v_{ij}}{2}-Rev(j)])]\right)x^*_{ij}(v_i,v_{-i}')$$


We here used the fact that expected value of product of negatively correlated variables is less than product of their expectations, and that expected revenue from item $j$ $Rev_j\geq \EE max_{k\neq i} b_j(v)$. Taking expectation over $v_i$ and $v_{-i}'$ (and removing primes from variables' names) we get

$$\EE_{v\sim F(v)}u_i(b^*(v_i,v_{-i}'),v_{-i}) \geq \EE_{v_i\sim F_i(v)\ \forall i} \sum_j \left ( \frac{v_{ij}}{2}-Rev(j)]\right)x^*_{ij}(v_i,v_{-i}')$$

Now we can sum up over $i$ and use the fact that distribution in expectation is the same to bring it out of the sum

$$\EE_{v\sim F(v)}\sum_i u_i(b^*(v_i,v_{-i}'),v_{-i}) = \EE_{v_i\sim F_i(v)\ \forall i}W_{opt}(v) - Rev(b)$$

Together with Conjecture 3.1 this gives POA of $1/4$.
